High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-01 paper/main.tex
finished going through methods section, outlined results section rewrite in comments

\paragraph{Hierarchical topographic factor analysis (HTFA).}
Following our prior related work, we used HTFA~\citep{MannEtal18} to
derive a compact representation of the data.  In brief, this approach
approximates the timeseries of voxel activations (44,415 voxels) using
a much smaller number of radial basis function nodes (in this case 700
nodes).  This provides a convenient representation for examining
full-brain network dynamics.  All of the analyses we carried out on
the neuroimaging dataset were performed in this lower-dimensional
space.  In other words, each participant's data matrix,
$\mathbf{Y}_0$, was a number-of-timepoints by 700 matrix of
HTFA-derived factor weights (where the row and column labels were
matched across participants).  Code for carrying out HTFA on fMRI data
may be found as part of the BrainIAK toolbox~\citep{brainiak}, which
may be downloaded at \href{https://brainiak.org/}{brainiak.org}.

@@

\textbf{JRM STOPPED HERE}

\subsubsection*{Reverse inference}
top 10 strongest correlations for each level; identify endpoint nodes
(RBFs); make map (threshold at $\theta$-- \textbf{JRM NOTE: what
  threshold did you use, Lucy?}); decode using neurosynth (cite).

\section*{Results}
\subsubsection*{Synthetic data}

>>>>

\paragraph{Hierarchical topographic factor analysis (HTFA).}
Following our prior related work, we used HTFA~\citep{MannEtal18} to
derive a compact representation of the data.  In brief, this approach
approximates the timeseries of voxel activations (44,415 voxels) using
a much smaller number of radial basis function (RBF) nodes (in this case 700
nodes).  This provides a convenient representation for examining
full-brain network dynamics.  All of the analyses we carried out on
the neuroimaging dataset were performed in this lower-dimensional
space.  In other words, each participant's data matrix,
$\mathbf{Y}_0$, was a number-of-timepoints by 700 matrix of
HTFA-derived factor weights (where the row and column labels were
matched across participants).  Code for carrying out HTFA on fMRI data
may be found as part of the BrainIAK toolbox~\citep{brainiak}, which
may be downloaded at \href{https://brainiak.org/}{brainiak.org}.

@@

\subsubsection*{Reverse inference}
The dynamic patterns we examine comprise high-dimensional correlation
patterns at each timepoint.  To help interpret the resulting patterns
in the context of other studies, we created summary maps by computing
the across-timepoint average pairwise correlations at each order of
analysis (first order, second order, etc., up to fifteenth order
correlations).  We selected the 10 strongest (absolute value)
correlations at each order.  Each correlation is between the dynamic
activity patterns (or patterns of dynamic high-order correlations)
measured at two RBF nodes (see \textit{Hierarchical Topographic Factor
  Analysis}).  Therefore, the 10 strongest correlations involved up to
20 RBF nodes.  Each RBF defines a spatial function whose activations
range from 0 to 1.  We thresholded each RBF at 0.999 to construct a
map of spherical components that denoted the endpoints of the 10
strongest correlations.  We then carried out a meta analysis using
Neurosynth~\citep{RubiEtal17} to identify the 10 terms most commonly
associated with the given map.  This resulted in a set of 10 terms
associated with the average dynamic correlation patterns at each order.

\section*{Results}
\textbf{JRM STOPPED HERE}

%overview: first validate our approach with synthetic data, then apply
%to fMRI data

%synthetic data: we can recover dynamic correlations using different
%kernels
% wider kernels (Laplace, Gaussian) performed best when the
% correlations varied in a temporally structured way
% delta function kernels were best when the correlations varied
% randomly over time
% overall we recovered the structure we embedded in the data under all
% synthetic datasets we tested.  our approach performed best when the
% underlying correlational structure was either constant or gradually
% changing.  our approach performed worst when the underlying
% correlations varied randomly for one timepoint to the next.

% we used temporal decoders to identify cognitivly relevant neural
% patterns in fMRI data (see forward inference section of methods).
% we explored two approaches to effiently computing high-order
% correlations: PCA (dimensionality reduction) and eigenvector
% centrality (graph measure).  both approaches yielded qualitatively
% similar results for the story listening conditions: intact story was
% best decoded using high-order correlations, whereas scrambled
% stories were best decoded using lower-order correlations.  both
% approaches also yielded slightly above-chance decoding of resting state times
% (perhaps picking up on decreasing attention and/or increasing
% mind-wandering as the resting state scan progressed).  The PCA-based
% approach achieved the highest decoding accuracy using
% non-correlational (activation-based) data, whereas the eigenvector
% centrality approach identified second-order correlations as being
% most informative about resting state times.

% finally, we sought to identify which specific brain areas were
% involved in supporting cognition through high-order interactions.
% we used the eigenvector centrality results, which preserves the
% original feature space when characterizing high-order dynamic
% correlations.  we found that first and second-order correlations
% reflected auditory and speech processing in all of the story
% listening conditions.  during intact story listening, third order
% correlations reflected integration with visual areas, and fourth
% order correlations recruited high-level cognition regions.  however,
% during listening to temporally scrambled stories, these higher-order
% correlations did not involve visual areas or high-order cognitive
% control regions.  during rest we found a much different set of
% patterns.  first order correlations involved counting networks; second-order
% correlations recruited visual networks; third-order correlations
% recruited working memory networks; fourth-order correlations
% recruited episodic memory areas.

\subsubsection*{Synthetic data}
